\chapter{Do I need a Chapter Title?}

Here I can reference the section on Chapter 2 (see.~\ref{sec_label}). To add reference open the bibliography file in TexStudio. Then you can cite in whatever manner you wish~\citet{Agn2007} or like~\citep{Choi2005,Dasari2000,frisch1995}

Piled Higher and Deeper - Life (or the lack thereof) in Academia (also known as PhD Comics),[1] is a newspaper and web comic strip written and drawn by Jorge Cham that follows the lives of several grad students. First published in the fall of 1997 when Cham was a grad student himself at Stanford University, the strip deals with issues of life in graduate school, including the difficulties of scientific research, the perils of procrastination, the complex student–supervisor relationship and the endless search for free food. Cham continued the strip as an Instructor in mechanical engineering at Caltech, and now draws and gives talks about the strip full time. Originally, the strip was drawn in crude black-and-white, eventually became grayscale, and finally became color in June 2004.

\section{Section to be labelled}  \label{sec_label}
Second chapter goes on \dots

I can also have some more references here \dots can't I? \citet{Gallouat2010}.

Here I have listed it as \citep[see][]{mehta1994}

Piled Higher and Deeper - Life (or the lack thereof) in Academia (also known as PhD Comics),[1] is a newspaper and web comic strip written and drawn by Jorge Cham that follows the lives of several grad students. First published in the fall of 1997 when Cham was a grad student himself at Stanford University, the strip deals with issues of life in graduate school, including the difficulties of scientific research, the perils of procrastination, the complex student–supervisor relationship and the endless search for free food. Cham continued the strip as an Instructor in mechanical engineering at Caltech, and now draws and gives talks about the strip full time. Originally, the strip was drawn in crude black-and-white, eventually became grayscale, and finally became color in June 2004.

\section{Without specifying width for last column:}
\begin{table}[h]
\caption{Table column width}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Day & Min Temp & Max Temp & Summary \\ \hline
    Monday & 11C & 22C & A clear day with lots of sunshine.
    However, the strong breeze will bring down the temperatures. \\ \hline
    Tuesday & 9C & 19C & Cloudy with rain, across many northern regions. Clear spells
    across most of Scotland and Northern Ireland,
    but rain reaching the far northwest. \\ \hline
    Wednesday & 10C & 21C & Rain will still linger for the morning.
    Conditions will improve by early afternoon and continue
    throughout the evening. \\    \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
    \hline
    Day & Min Temp & Max Temp & Summary \\ \hline
    Monday & 11C & 22C & A clear day with lots of sunshine.  
    However, the strong breeze will bring down the temperatures. \\ \hline
    Tuesday & 9C & 19C & Cloudy with rain, across many northern regions. Clear spells
    across most of Scotland and Northern Ireland,
    but rain reaching the far northwest. \\ \hline
    Wednesday & 10C & 21C & Rain will still linger for the morning.
    Conditions will improve by early afternoon and continue
    throughout the evening. \\ \hline
    \end{tabular}
\end{center}
\end{table}


\section{Multiple columns}
\begin{table}[h]
\caption{Multiple Columns}
\begin{tabular}{l|*{6}{c}|r|}
Team              & P & W & D & L & F  & A & Pts \\
\hline
Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
FC Copenhagen     & 6 & 2 & 1 & 2 &  5 & 8 &  7  \\
\end{tabular}
\end{table}

